---
title: "Cardiovascular Point-of-Care Ultrasonography and Resident Learning"
author:
- Anish Shah, MD^[Department of Medicine, School of Medicine, Emory University, Atlanta,
  Georgia]
- Mikhail Akbashev, MD^[Department of Medicine, School of Medicine, Emory University,
  Atlanta, Georgia]
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  word_document:
    highlight: tango
    reference_docx: word_style.docx
header-includes:
  - \usepackage{dcolumn}
  - \usepackage{float}
  - \usepackage{graphicx} 
editor_options: 
  chunk_output_type: console
always_allow_html: yes
csl: american-medical-association.csl
bibliography: medical_education.bib
---

```{r setup, global_options, include = FALSE}
knitr::opts_chunk$set(
  cache = TRUE,
  warning = FALSE,
  eval = TRUE,
  echo = FALSE,
  include = FALSE,
  message = FALSE,
  options(scipen = 999, digits = 3)
)

options(
  xtable.table.placement = "H",
  xtable.comment = FALSE
)
```

```{r}
# Libraries
source("1_libraries.R")

# Date intake
source("2_intake.R")

# Data tidying
source("3_tidy.R")
```

# Methods

The cohorts were divided by class years, from recent graduates of the program to current PGY3, PGY2, and PGY1. The data was acquired from 06/2018 to 08/2019. The population sampled was `r n_GRAD + n_PGY3 + n_PGY2 + n_PGY1` residents (including recent grads).

The response rates per group is shown. The surveys were sent from June 2018 to August 2018. 

| Cohort | n | Response (%) |
| --- | --- | --- |
| GRAD | `r n_GRAD` | `r length(demo$id[demo$cohort=="GRAD"])/n_GRAD * 100 ` |
| PGY3 | `r n_PGY3` | `r length(demo$id[demo$cohort=="PGY3"])/n_PGY3 * 100 ` |
| PGY2 | `r n_PGY2` | `r length(demo$id[demo$cohort=="PGY2"])/n_PGY2 * 100 ` |
| PGY1 | `r n_PGY1` | `r length(demo$id[demo$cohort=="PGY1"])/n_PGY1 * 100 ` |

## Quiz breakdown

The quiz was broken down into several sections. There were 5 targeted areas for the survey.

- Cardiovascular view identification
- Cardiovascular structure identification
- Cardiovascular function assessment (e.g. ejection fraction)
- Vascular structure identification (e.g. IVC, aorta)
- Vascular function assessment (e.g. collapsibility of IVC)

The responses are in the form of a percent by each cohort, so within cohort comparisons can be assessed.

## Overconfidence

Residents also labeled their confidence in their answer choices. Four categories were devised representing POCUS knowledge and confidence in decision-making.

| | Confident | Not Confident |
| --- | --- | --- | 
| Correct | Understanding | Underconfident |
| Incorrect | Overconfident | Knowledge Gap |

# Results

## Baseline characteristics

```{r baseline characterisics}
# Data set
df <- demo

# Compare groups
cmp_baseline <- 
  compareGroups(cohort ~ curriculum + experience + comfort_dx + comfort_tx + interest_level + proc_career, data = df) %>% 
  createTable(., show.n = F, show.ratio = F, show.p.overall = F)
```

There were a total of `r nrow(df)` participants in the study, including PGY1 (n=`r nrow(df[df$cohort == "PGY1",])`), PGY2 (n=`r nrow(df[df$cohort == "PGY2",])`), PGY3 (n=`r nrow(df[df$cohort == "PGY3",])`), and recent graduates (n=`r nrow(df[df$cohort == "GRAD",])`). There was >80% self-reported interest in POCUS, with over >60% expressing interest in a procedural career, and <30% having prior experience in POCUS. Further breakdown by cohort is seen in __Table 1__.

## Point-of-care ultrasonography knowledge 

```{r score by class}
# Data
df <- inner_join(demo, df_scores) %>% 
  compareGroups(cohort ~ percent, data = .) %>%
  createTable(., show.n = F, show.ratio = F, show.p.overall = F)
```

The mean percent score (SD) on the questionnaire was `r mean(na.omit(df_scores$percent))` (`r sd(na.omit(df_scores$percent))`). By cohort, the PGY1 class scored `r df$descr[1,1]`, the PGY2 class scored `r df$descr[1,2]`, the PGY3 class scored `r df$descr[1,3]`, and the recent graduates scored `r df$descr[1,4]`. The questions were further broken down by type, as seen in __Figure XXX___.

```{r t-test}
# Data 
df <- inner_join(demo, df_scores)

# Curriculum
tcur <- t.test(
  df$percent[df$curriculum == "Yes"],
  df$percent[df$curriculum == "No"]
)

# Cohorts
tcoh12 <- t.test(
  df$percent[df$cohort == "PGY1"],
  df$percent[df$cohort == "PGY2"]
)
tcoh13 <- t.test(
  df$percent[df$cohort == "PGY1"],
  df$percent[df$cohort == "PGY3"]
)
tcoh1g <- t.test(
  df$percent[df$cohort == "PGY1"],
  df$percent[df$cohort == "GRAD"]
)
tcoh23 <- t.test(
  df$percent[df$cohort == "PGY2"],
  df$percent[df$cohort == "PGY3"]
)
tcoh2g <- t.test(
  df$percent[df$cohort == "PGY2"],
  df$percent[df$cohort == "GRAD"]
)
tcoh3g <- t.test(
  df$percent[df$cohort == "PGY3"],
  df$percent[df$cohort == "GRAD"]
)
```

There was a difference in scores after completion of the curriculum (p = `r tcur$p.value`), as seen in __Figure XXX__.  

## Confidence levels

```{r confidence overview}
# Data frame
df <- inner_join(df_overconfidence, demo, by = "id") %>%
  inner_join(., quiz_guide, by = "question") %>%
  na.omit()

# For basic overview
tmp <- df_concordance$confidence %>% na.omit()
tconf <- prop.table(table(df_overconfidence$level)) * 100
tlevel <- prop.table(table(df$level, df$curriculum), margin = 1) * 100

# Comparison table
cmp_confidence <- compareGroups(level ~ cohort + curriculum, data = df) %>%
  createTable(., show.n = FALSE, show.ratio = FALSE, show.p.overall = FALSE)

# Basic overview of confidence
inner_join(df_concordance, demo, by = "id") %>%
  compareGroups(correctness ~ cohort, data = .) %>%
  createTable(., show.n = FALSE, show.ratio = FALSE, show.p.overall = FALSE)
```

Overall, participants reported being confident on `r mean(tmp)`% (`r sd(tmp)`) questions. When compared with their individual answer choices, `r tconf[1]`% demonstrated a _Knowledge Gap_, `r tconf[2]`% demonstrated _Overconfidence_, `r tconf[3]`% demonstrated _Underconfidence_, and `r tconf[4]`% demonstrated _Understanding_. This is further delineated in __Table 2__, including by presence of the curriculum. Of note, although there was an increase in _Understanding_ from `r tlevel[4,1]`% to `r tlevel[4,2]` after the curriculum, there was also an increase in _Overconfidence_ from `r tlevel[2,1]`% to `r tlevel[2,2]`%. The distrubtion of confidence by question type is seen in __Figure XXX__.

## Regression Analysis

```{r}
# Data
df <- inner_join(df_overconfidence, demo, by = "id") %>% na.omit()
df$level %<>% factor()

# Initial regressions
mcur <- clmm(level ~ curriculum + (1|id), data = df)
mcoh <- clmm(level ~ cohort + (1|id), data = df)
mint <- clmm(level ~ curriculum + cohort + curriculum:cohort + (1|id), data = df)

tmp <- summary(mcur)
```

Curriculum was found to be significant in affecting congruence between confidence and competence (p = `r tmp$coefficients[4,4]`). Completion of curriculum had an OR = `r exp(coef(mcur)[4])` (95% confidence interval (CI) = `r exp(confint(mcur))[4,1]`, `r exp(confint(mcur))[4,2]`) of demonstrating _Understanding_ over other categories (e.g. _Overconfidence_). In an additional model adjusted for cohort, there was a significant negative interaction between curriculum and cohort year (p = `r summary(mint)$coefficients[9,4]`).

# Tables

## Table 1

```{r}
export2csv(cmp_baseline, file = "table1.csv")
```

## Table 2

```{r}
export2csv(cmp_confidence, file = "table2.csv")
```


# Figures

## Figure XXX

```{r plot score by type of question}
# data
df <-
  gather(df_scores[-c(22,23)], key = "question", value = "score", -id) %>%
  inner_join(., quiz_guide, by = "question") %>%
  inner_join(demo[c("id", "cohort")], ., by = "id")

# Relabel the question types
df$question_type %<>% factor()
levels(df$question_type) <- c("LVEF", "CV Anatomy", "US View", "Volume", "Vasc Strx")
  
# Score by group
ggplot(data = na.omit(df), aes(x = cohort, y = score, fill = cohort)) + 
  stat_summary(fun.y = "mean", geom = "bar") +
  scale_y_continuous(labels = percent) + 
  facet_wrap(~question_type, ncol = 1, scales = "free_x") + 
  scale_fill_viridis_d() + 
  theme_minimal() +
  theme(
    legend.position = "none"
  ) +
  labs(
    title = "Scores within each question type",
    x = "Cohort",
    y = "Percentage"
  )
```

## Figure XXX

```{r fig cohort scores}
# Combine scores and demographic information
df <- full_join(demo[c("id", "cohort", "curriculum", "proc_career")], df_scores, by = "id") %>% na.omit()

# Comparisons for box plot
my_comp <- list(c(1,2), c(2,3), c(3,4), c(1,4))

# X axis, change to numeric and add labels later
# This is to add a V-line for the curriculum
levels(df$cohort) <- c(1,2,3,4)

# GGpubr version for ease
ggboxplot(na.omit(df), x = "cohort", y = "percent", fill = "cohort") +
  scale_fill_viridis_d() + 
  stat_compare_means(comparisons = my_comp, label = "p.signif", method = "t.test") + 
  labs(
    title = "Training cohorts and quiz accuracy",
    x = "Level of training",
    y = "Percent correct"
  ) +
  theme_minimal() + 
  rremove("legend") +
  scale_x_discrete(labels = c("1" = "PGY1", "2" = "PGY2", "3" = "PGY3", "4" = "GRAD")) +
  geom_vline(xintercept = 2.4, linetype = "dashed", color = "indianred", size = 0.5) +
  geom_text(aes(x = 2.7, y = 40, label = "Curriculum\nIntervention"), colour = "indianred")
```

## Figure XXX

```{r fig confidence by curriculum}
# Combine confidence and cohort population
df <- 
  inner_join(demo[c("id", "cohort", "curriculum")], df_overconfidence, by = "id") %>%
  inner_join(quiz_guide, ., by = "question") %>%
  na.omit()

# Relabel the question types
df$question_type %<>% factor()
levels(df$question_type) <- c("LVEF", "CV Anatomy", "US View", "Volume", "Vasc Strx")

# Visualize by curriculum
ggplot(df, aes(x = curriculum, fill = level)) + 
  facet_wrap(~question_type, ncol = 1, scale = "free_y") + 
  geom_bar(aes(y = ..count../sum(..count..)), position = "dodge") + 
  scale_y_continuous(labels = percent) + 
  labs(
    title = "Confidence Levels by Curriculum",
    x = "Completion of curriculum",
    y = "Percent"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom"
    ) +
  scale_fill_viridis_d(name = "Confidence Levels", labels = c("Knowledge Gap", "Overconfidence", "Underconfidence", "Understanding"))
```

## Supplemental Figure XXX

```{r fig confidence v accuracy}
# Data
df <- gather(df_concordance[c("id", "question", "correctness", "confidence")], key = "measure", value = "value", -id, -question) %>%
  inner_join(demo, ., by = "id") %>%
  na.omit()

# Visualize confidence and accuracy by curriculum
ggplot(df, aes(x = question, fill = measure)) +
  facet_wrap(~curriculum) +
  geom_bar(aes(y = value), position="dodge", stat = "summary", fun.y = "mean") +
  scale_fill_viridis_d(begin = .2) + 
  scale_y_continuous(labels = percent) + 
  theme_minimal() +
  labs(
    title = "Confidence and accuracy by curriculum introduction",
    x = "Questions",
    y = "Proportion"
  ) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

